Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-07-03 doc/manuscript/manuscript.Rmd
add AMOVA table to manuscript

>>>>

-------------------------------------------------------------------------------
Hierarchy               d.f.        S.S.       % variation    $\Phi statistic$  
-------------------- ---------- ------------- -------------- ------------------
Between Source         1 (1)    0.897 (0.753) -0.158 (0.116)   0.136 (0.0965)

Between Region        20 (19)     12 (8.91)    13.8 (9.53)     **0.138 (0.0955)**   
within Source

Within Region        296 (282)   56.7 (55.1)   86.4 (90.3)   **-1.58e^-3^ (1.16e^-3^)**

-------------------------------------------------------------------------------

Table: (\#tab:amova) Analysis of Molecular Variance showing little differentiation between White Mold Nurseries and other sources. The hierarchy was constructed as Source/Region where source is defined as belonging to a white mold nursery or not. Bold $\Phi$ values indicate significant values. Numbers in parentheses represent AMOVA run without Mexican isolates included. S.S. = Sum of Squares, d.f. = degrees of freedom.
